Using Scagnostics to find Interesting Projections of Multivariate Data

### 2018-09-19 scagnostics.Rmd
References added, start using neutron star data as example.

# Scagnostics indices
\label{sec:indexes}

## Individual

## Two group differences

## Multiple group differences

# Application to particle physics data
\label{sec:phys}

## Data description

## Software setup

## Scagnostics of grand tour projections

>>>>

# Application to physics data
\label{sec:phys}

We now want to apply the developped tools to distributions from realistic physics application. Here we choose as an example to use posterior samples obtained when fitting source parameters to the observed gravitatioal wave signal GW170817 @PhysRevLett119161101. The fit details were described in @Abbott2018exr and the corresponding data is available online @ligoData.

## Data description
The model describes a neutron star merger and contains 6 free parameters, i.e. each neutron star is described by its mass and radius, and a so-called tidal deformability parameter $\Lambda$. A posterior sample containing 2538 points is available @ligoData and can be used to constrain the parameters. For details about the modelling and statistical procedure see @Abbott2018exr.
Show corner plot here, comment on well constrained relation between m1 and m2 ("chirp mass")
For further study we therefore remove m2 from the dataset and use the guided tour working with the remaining 5 dimensions.

Use spline2d index, find relation between 3 parameters, ask Rory for interpretation

## Higher D
To complicate things can work with bigger dataset that Rory sent me, need to check if this is public, also need help with interpretation, but here optimising TIC finds interesting projection
